---
output:
  github_document:
    html_preview: false
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

## Overview

The package `"binomial"` is an [R](http://www.r-project.org/) package that provides functions to view and visualize the binomial distribution as well as view characteristics of the distribution.

This package includes the following functions:

* bin_choose() finds the number of ways in which k successes can occur in n trials.
* bin_probability() finds the probability of getting k successes in n trials for a binomial distribution.
* bin_distribution() finds the entire probability distribution of a binomial random variable. The distribution can also be plotted using plot.bindis().
* bin_cumulative() finds the entire cumulative probability distribution of a binomial random variable. The distribution can also be plotted using plot.bincum().
* bin_variable() returns a list specifying the number of trials and the probability of success for a binomial random variable.summary.binvar() allows you to view the summary statistics of the random variable.
* bin_mean() finds the mean of a binomial random variable.
* bin_variance() finds the variance of a binomial random variable.
* bin_mode() finds the mode of a binomial random variable.
* bin_skewness() finds the skewness of a binomial random variable.
* bin_kurtosis() finds the kurtosis of a binomial random variable.

## Motivation 

This package has been developed as part of a project for Statistics 133.

## Installation

Install the development version from GitHub via the package `"devtools"`:

``` r
# development version from GitHub:
#install.packages("devtools") 
# install "binomial" (without vignettes)
devtools::install_github("stat133-sp19/hw-stat133-nsharma1998binomial")
# install "binomial" (with vignettes)
devtools::install_github("stat133-sp19/hw-stat133-nsharma1998/binomial", build_vignettes = TRUE)
```

## Usage

```{r}
library(binomial)

# 55 heads in 100 tosses of a loaded coin with 45% chance of heads
bin_probability(success = 55, trials = 100, prob = 0.45)
 

# binomial probability distribution
bin_distribution(trials = 5, prob = 0.5)


#binomial cumulative distribution
bin_cumulative(trials = 5, prob = 0.5)
 

#Binomial with n=10, p=0.3
bin_mean(10, 0.3)
bin_variance(10, 0.3)
bin_mode(10, 0.3)
bin_skewness(10, 0.3)
bin_kurtosis(10, 0.3)
